Spatiotemporal clusters in the CSD-CM representation

### 2019-09-04 Reportes/clusteringkarel.tex
hay que ponerle el exp a la tabla

We decided to use a certain ``aesthetic'' criterium for choosing the optimal parameters
for the DBSCAN algorythm.  It is its accordance with Zipf's Law.  This could post out
the accordance with the allometric inverse algebraic laws that are observed in
anatomical studies, but it is, in the end, a somewhat arbitrary criterium.
Nevertheless, a good
fit with Zipfs Law could be an indictor of a natural clustering of data points.
A problem that appeard using this criterium is that it is such a pervarsive
behaviour of ranked data
that it gives a good fit to allmost any set of reazonable parameters
that one encounters. So we had to come up with criteria for what these ``reasonable
parameters'' may be.  We settled that we shouldn't have to many unasigned points, and
that no cluster should be too big, or that there were to many clusters.

@@

\begin{tabular}{|r|r|r|r|r|r|}
 radius &  n  & $R^2$ & u & m & ng  \\ \hline
  1 &  2 &  0.978 & 606 & 606 & 1285 \\
  1 &  3 &  0.984 & 1346 & 1346 & 915 \\
  1 &  4 &  0.974 & 2300 & 2300 & 658 \\
  1 &  5 &  0.951 & 3193 & 3193 & 493 \\
  1 &  6 &  0.918 & 4023 & 4023 & 375 \\
  1.5 &  2 &  0.987 & 276 & 1007 & 691 \\
  1.5 &  3 &  0.987 & 660 & 1007 & 499 \\
  1.5 &  4 &  0.985 & 1060 & 1060 & 391 \\
  1.5 &  5 &  0.986 & 1523 & 1523 & 315 \\
  1.5 &  6 &  0.99 & 2040 & 2040 & 258 \\
  2 &  2 &  0.95 & 156 & 5355 & 343 \\
  2 &  3 &  0.928 & 382 & 5355 & 230 \\
  2 &  4 &  0.912 & 566 & 5349 & 174 \\
  2 &  5 &  0.906 & 777 & 5308 & 132 \\
  2 &  6 &  0.915 & 976 & 3734 & 112 \\
  2.5 &  2 &  0.911 & 113 & 6144 & 225 \\
  2.5 &  3 &  0.875 & 243 & 6144 & 160 \\
  2.5 &  4 &  0.849 & 349 & 6142 & 127 \\
  2.5 &  5 &  0.828 & 475 & 6127 & 100 \\
  2.5 &  6 &  0.849 & 602 & 6008 & 81 \\
  3 &  2 &  0.909 & 89 & 7408 & 163 \\
  3 &  3 &  0.874 & 187 & 7408 & 114 \\
  3 &  4 &  0.847 & 267 & 7404 & 89 \\
  3 &  5 &  0.829 & 343 & 7402 & 71 \\
  3 &  6 &  0.817 & 418 & 7400 & 58 
\end{tabular}

>>>>

We decided to use a certain ``aesthetic'' criterium for choosing the optimal parameters
for the DBSCAN algorythm.  It is its accordance with Zipf's Law.  This could post out
the accordance with the allometric inverse algebraic laws that are observed in
anatomical studies, but it is, in the end, a somewhat arbitrary criterium.
Nevertheless, a good
fit with Zipfs Law could be an indictor of a natural clustering of data points.
A problem that appeard using this criterium is that it is such a pervarsive
behaviour of ranked data
that it gives a good fit to allmost any set of reazonable parameters
that one encounters. So we had to come up with criteria for what these ``reasonable
parameters'' may be.  We settled that we shouldn't have to many unasigned points, and
that no cluster should be too big, or that there were to many clusters. In the
table \ref{tablarquad} we show the fitting results for some values of
$r$ and $n$. The model that was fitted did not specify the exponent, it
is remarkable how the various models gave values for this parameter so close
to the ideal $-1$.

@@

\begin{center}
\begin{tabular}{|r|r|r|r|r|r|}
 r &  n  & $R^2$ & u & m & ng  \\ \hline
  1 &  2 &  0.978 & 606 & 606 & 1285 \\
  1 &  3 &  0.984 & 1346 & 1346 & 915 \\
  1 &  4 &  0.974 & 2300 & 2300 & 658 \\
  1 &  5 &  0.951 & 3193 & 3193 & 493 \\
  1 &  6 &  0.918 & 4023 & 4023 & 375 \\
  1.5 &  2 &  0.987 & 276 & 1007 & 691 \\
  1.5 &  3 &  0.987 & 660 & 1007 & 499 \\
  1.5 &  4 &  0.985 & 1060 & 1060 & 391 \\
  1.5 &  5 &  0.986 & 1523 & 1523 & 315 \\
  1.5 &  6 &  0.99 & 2040 & 2040 & 258 \\
  2 &  2 &  0.95 & 156 & 5355 & 343 \\
  2 &  3 &  0.928 & 382 & 5355 & 230 \\
  2 &  4 &  0.912 & 566 & 5349 & 174 \\
  2 &  5 &  0.906 & 777 & 5308 & 132 \\
  2 &  6 &  0.915 & 976 & 3734 & 112 \\
  2.5 &  2 &  0.911 & 113 & 6144 & 225 \\
  2.5 &  3 &  0.875 & 243 & 6144 & 160 \\
  2.5 &  4 &  0.849 & 349 & 6142 & 127 \\
  2.5 &  5 &  0.828 & 475 & 6127 & 100 \\
  2.5 &  6 &  0.849 & 602 & 6008 & 81 \\
  3 &  2 &  0.909 & 89 & 7408 & 163 \\
  3 &  3 &  0.874 & 187 & 7408 & 114 \\
  3 &  4 &  0.847 & 267 & 7404 & 89 \\
  3 &  5 &  0.829 & 343 & 7402 & 71 \\
  3 &  6 &  0.817 & 418 & 7400 & 58 
\end{tabular}
\caption{Table of $R^2$ values fitting Zipf's Law to the clustering
  rank and size for various parameters. Here $r$ is the neighborhood
  radius, $n$ the number of required neighboors including itself,
  $R^2$ is the coefficient of determination, $u$ is the number of
  unasigned points, $m$ the size in points of the largest
  cluster, and $ng$ the number of clusters. }
\label{tablarquad}
\end{center}
